Latest developments on the highly granular Silicon-Tungsten Electromagnetic Calorimeter technological prototype for the International Large Detector.

### 2019-04-04 proceedings/IEEE2017/proceeding_v3.tex
create folder for all confereces (2017)

\begin{figure}[!t]
\centering
\includegraphics[width=3.0in]{shortslab-eps-converted-to.pdf}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Open single SLAB with FEV11 ASU, 16 SKIROC, interface card and DIF visibles. The silicon sensors are glued to the PCB in the other side.}
\label{shortslab}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=3.0in]{fevcob1-eps-converted-to.pdf}\\
    \includegraphics[width=3.0in]{fevcob2-eps-converted-to.pdf}
  \end{tabular}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Photograph of the FEV11\_COB. The first figure correspond to a picture taken from the top. The second one is a lateral picture.}
\label{fevcob}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3.0in]{proto-eps-converted-to.pdf}
\caption{Technological prototype: 7 single short slabs inside the mechanical aluminum structure.}
\label{prototype}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=2.5in]{mipsummary-eps-converted-to.pdf}  \\
    \includegraphics[width=2.5in]{snsummary-eps-converted-to.pdf}
  \end{tabular}
\caption{Result of the MIP position calculation and signal over noise calculation for all calibrated cells.}
\label{mipandSN}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{mip3peaks-eps-converted-to.pdf}
\caption{Single cell energy distribution (for all calibrated cells) for 3 GeV positron tracks acting as MIPs. }
\label{miplog}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=3.0in]{shower1-eps-converted-to.pdf}\\
    \includegraphics[width=3.0in]{shower2-eps-converted-to.pdf}\\
    \includegraphics[width=3.0in]{shower3-eps-converted-to.pdf}
  \end{tabular}
\caption{Raw electromagnetic shower profiles for three different tungsten configurations. In the x-axis, we show the layer number. In the y-axis, the averaged fraction of {\it energy} (sum of ADC in all triggered cells in a event, considering only events where all layers had at least a hit) measured in every layer. }
\label{showers}
\end{figure}

@@

%%--
\begin{figure}[!t]
\centering
\includegraphics[width=2.0in]{longslab-eps-converted-to.pdf}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Design of a long layer being currently produced.}
\label{longslab}
\end{figure}

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=3.0in]{shortslab.eps}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Open single SLAB with FEV11 ASU, 16 SKIROC, interface card and DIF visibles. The silicon sensors are glued to the PCB in the other side.}
\label{shortslab}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=3.0in]{fevcob1.eps}\\
    \includegraphics[width=3.0in]{fevcob2.eps}
  \end{tabular}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Photograph of the FEV11\_COB. The first figure correspond to a picture taken from the top. The second one is a lateral picture.}
\label{fevcob}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3.0in]{proto.eps}
\caption{Technological prototype: 7 single short slabs inside the mechanical aluminum structure.}
\label{prototype}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=2.5in]{mipsummary.eps}  \\
    \includegraphics[width=2.5in]{snsummary.eps}
  \end{tabular}
\caption{Result of the MIP position calculation and signal over noise calculation for all calibrated cells.}
\label{mipandSN}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{mip3peaks.eps}
\caption{Single cell energy distribution (for all calibrated cells) for 3 GeV positron tracks acting as MIPs. }
\label{miplog}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=3.0in]{shower1.eps}\\
    \includegraphics[width=3.0in]{shower2.eps}\\
    \includegraphics[width=3.0in]{shower3.eps}
  \end{tabular}
\caption{Raw electromagnetic shower profiles for three different tungsten configurations. In the x-axis, we show the layer number. In the y-axis, the averaged fraction of {\it energy} (sum of ADC in all triggered cells in a event, considering only events where all layers had at least a hit) measured in every layer. }
\label{showers}
\end{figure}

@@

%%--
\begin{figure}[!t]
\centering
\includegraphics[width=2.0in]{longslab.eps}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Design of a long layer being currently produced.}
\label{longslab}
\end{figure}
